Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-07 paper.qmd
typo

[^pax]: `pax` values, i.e. number of passengers, will be used for future work on
        casuality risk calculation.

@@

Future work will address the derivation of casuality expectation using
seats information for aircraft types in the traffic.
<!-- or can we say something about the next concrete steps to remedy some weaknesses -->

>>>>

[^pax]: `pax` values, i.e. number of passengers, will be used for future work on
        casualty risk calculation.

@@

Future work will address the derivation of casualty expectation using
seats information for aircraft types in the traffic.
<!-- or can we say something about the next concrete steps to remedy some weaknesses -->
